Hierarchical Reverberation Mapping

### 2013-10-25 Paper/ms.tex
New CCF figure
Don't know what to say about ccf

The cross correlation function, as a function of lag $\tau$, is then defined as:
\begin{eqnarray}
\textnormal{CCF}(\tau) =
\sum_{i=1}^{N_c} \sum_{j=1}^{N_l}
\left(\frac{(y_i - \bar{y})(l_j - \bar{l})}{\sigma_{y_i}^2\sigma_{l_j}^2}
\delta\left[\tau - (t_{l_j} - t_{y_i})\right]\right)
\end{eqnarray}
This can be understood as a set of delta-function spikes, one for each pair
of points (one point chosen from the continuum data, and one point from the
line data). The position of each spike depends on the time between the continuum
data point and the line data point, and the mass of each spike is proportional
to the continuum and line fluxes.

The stacked cross-correlation function for $N$ objects is the mean of the CCFs
of the individual objects, after normalising each object's CCF to unity.
\begin{eqnarray}
\textnormal{SCCF}(\tau) &=&
\frac{1}{N} \sum_{i=1}^N
\left(
\frac{\textnormal{CCF}_i(\tau)}{\int \textnormal{CCF}_i(\tau) \, d\tau}
\right)
\end{eqnarray}
Since the CCF definition involves delta-functions, some smoothing is necessary
to display the stacked CCF. In Figure~\ref{fig:ccf},
we show the stacked CCF from the 100 simulated AGN data sets, plotted as a
histogram (the nonzero bin width provides the smoothing).

>>>>

The cross correlation function, as a function of lags $\tau$, is then defined as:
\begin{eqnarray}
\textnormal{CCF}(\tau) =
\sum_{i=1}^{N_c} \sum_{j=1}^{N_l}
\left(\frac{(y_i - \bar{y})(l_j - \bar{l})}{\sigma_{y_i}^2\sigma_{l_j}^2}
\delta\left[\tau - (t_{l_j} - t_{y_i})\right]\right)
\end{eqnarray}
This can be understood as a set of delta-function spikes, one for each pair
of points (one point chosen from the continuum data, and one point from the
line data). The position of each spike depends on the time between the continuum
data point and the line data point, and the mass of each spike is proportional
to the continuum and line fluxes.

The stacked cross-correlation function for $N$ objects is sum of the CCFs
of the individual objects.
\begin{eqnarray}
\textnormal{SCCF}(\tau) &=&
\frac{1}{N} \sum_{i=1}^N
\left(
\frac{\textnormal{CCF}_i(\tau)}{\int \textnormal{CCF}_i(\tau) \, d\tau}
\right)
\end{eqnarray}
In Figure~\ref{fig:ccf},
we show the stacked CCF from the 100 simulated AGN data sets.
